\LARGE \bf Budgeted Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty

### 2014-12-24 paper.tex
added sensitivity analysis, changed ordering of sections

@@

 To sample from $p(Q(\Gamma)>0)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\Delta,\theta, \rho)$. Using Bayes rule and our graphical model we can rewrite this as

 \vspace{-2ex}
 \begin{align*}
 &p(\textbf{n}_i,\textbf{c}_i |\gamma_i(t),\theta,\Delta,\rho)=\\
 &p(\textbf{n}_i|\textbf{c}_i,\theta)p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\Delta)
 \end{align*}

 In section \ref{sec:contact}, we look at how to draw shape sample from a GPIS model, which is used to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\Delta)$ along with the other sampled distribution on pose ($\Delta$) and motion ($\rho$). Then in section \ref{sec:normals}, we look at how to sample from $p(\textbf{n}_i|\textbf{c}_i,\theta)$ and present a novel visualization technique for the distribution on surface normals. Lastly in section \ref{sec:mass}, we show a way to calculate the expected center of mass assuming a uniform mass distribution. 
 .
\subsection{Distribution on Surface Normals}\label{sec:normals} 
Using Eq. \ref{eq:mean_gradient} and Eq. \ref{eq:cov_gradient}, we can compute the mean of the gradient $ \mu_{\nabla}(x)$ and the covariance of the gradient $\Sigma_{\nabla}(x)$ respectively. Thus we can compute the distribution around the surface normal for a given point in $\mathcal{W}$. We can now write

@@

\section{Multi-Armed Bandits for Grasp Selection}
While a standard approach to solving the problem in Eq. \ref{eq:problem_def} would be to perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-armed bandit model and forming a policy for selecting which grasp to sample. 
In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
Here each arm corresponds to a different grasp plan and pulling the arm is sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the arm's grasp plan on the sample.
The reward for pulling an arm is 1 if the grasp is in force closure on the sample and 0 if the grasp is not in force closure.

Since, we have framed the method as a Beta-Bernoulli problem we can use the methods in Sec.\ref{sec:algorithms} and obtain guarantees in the convergence properties of regret and overall performance of our policy for grasp allocation.

\section{Calculating the Probability of Force Closure}
Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P (\theta )$, the distribution on center of pose $P (\Delta)$, distribution on motion $p(\rho)$ and the distribution on friction coefficient $P (\mu)$. The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$. Thus, we can write the expected probability of force closure as follows

\vspace{-2ex}
\begin{align}\label{eq:shape_sampling}
P(Q(\Gamma|\theta,\mu,\Delta,\rho) > 0) = \frac{\alpha}{\alpha + \beta}
\end{align}

Where $Q(\Gamma|S,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(S)$,$p(\Delta)$,$p(\rho)$ and $p(\mu)$. To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating}, \cite{kehoe2012toward},  \cite{christopoulos2007handling}. Whats interesting in the context of a BMAB problem our complicated graphical model in Fig. \ref{fig:graphical_model}, can now be replaced by \ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality. It is this intuition that helps explain the performance of the BMAB algorithm.

@@

>>>>

\section{Multi-Armed Bandits for Grasp Selection}
While a standard approach to solving the problem in Eq. \ref{eq:problem_def} would be to perform Monte-Carlo integration on each $\Gamma_i$ and compute the probability of force closure, we propose treating the problem as a multi-armed bandit model and forming a policy for selecting which grasp to sample. 
In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
Here each arm corresponds to a different grasp plan and pulling the arm is sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the arm's grasp plan on the sample.
The reward for pulling an arm is 1 if the grasp is in force closure on the sample and 0 if the grasp is not in force closure.

Given a proposed grasp plan $\Gamma$ , we draw samples from the shape distribution $P (\theta )$, the distribution on center of pose $P (\xi)$, distribution on motion $p(\rho)$ and the distribution on friction coefficient $P (\mu)$. The distribution on force closure can then be estimated as Beta- Bernoulli Process with shape parameters $\alpha$ and $\beta$. Thus, we can write the expected probability of force closure as follows

\vspace{-2ex}
\begin{align}\label{eq:shape_sampling}
P(Q(\Gamma|\theta,\mu,\xi,\rho) > 0) = \frac{\alpha}{\alpha + \beta}
\end{align}

Where $Q(\Gamma|\theta,\xi,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(\theta)$,$p(\xi)$,$p(\rho)$ and $p(\mu)$. To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating}, \cite{kehoe2012toward},  \cite{christopoulos2007handling}. Whats interesting in the context of a BMAB problem our complicated graphical model in Fig. \ref{fig:graphical_model}, is now equivalent in terms of inference to \ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality. It is this intuition that helps explain the performance of the BMAB algorithm.

@@

 To sample from $p(Q(\Gamma)>0)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\xi,\theta, \rho)$. Using Bayes rule and our graphical model we can rewrite this as

 \vspace{-2ex}
 \begin{align*}
 &p(\textbf{n}_i,\textbf{c}_i |\gamma_i(t),\theta,\xi,\rho)=\\
 &p(\textbf{n}_i|\textbf{c}_i,\theta)p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\Delta)
 \end{align*}

 In section \ref{sec:Appendix}, we look at how to draw shape sample from a GPIS model, which is used to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ along with the other sampled distribution on pose ($\xi$) and motion ($\rho$). Then in section \ref{sec:normals}, we look at how to sample from $p(\textbf{n}_i|\textbf{c}_i,\theta)$ and present a novel visualization technique for the distribution on surface normals. Lastly in section \ref{sec:mass}, we show a way to calculate the expected center of mass assuming a uniform mass distribution. 
 .
\subsection{Distribution on Surface Normals}\label{sec:normals} 
Using Eq. \ref{eq:mean_gradient} and Eq. \ref{eq:cov_gradient}, we can compute the mean of the gradient $ \mu_{\nabla}(x)$ and the covariance of the gradient $\Sigma_{\nabla}(x)$ respectively. Thus we can compute the distribution around the surface normal for a given point in $\mathcal{W}$. We can now write

@@

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width = 16.5cm, height = 13cm]{matlab_figures/sensitivity_rot.eps}
\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Random, UCB, Thompson, Gittins). Graph is averaged over 100 shapes from the Brown Sillohoute Dataset \cite{brown} with a set $|G|=1000$ for each shape. As you can see the Thompson and Gittins method converge almost a magnitude faster than random allocation. UCB does poorly on simple regret which is expected \cite{best_arm}}
\vspace*{-10pt}
\label{fig:simple_regret}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width = 16.5cm, height = 13cm]{matlab_figures/sensitivity_trans.eps}
\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Random, UCB, Thompson, Gittins). Graph is averaged over 100 shapes from the Brown Sillohoute Dataset \cite{brown} with a set $|G|=1000$ for each shape. As you can see the Thompson and Gittins method converge almost a magnitude faster than random allocation. UCB does poorly on simple regret which is expected \cite{best_arm}}
\vspace*{-10pt}
\label{fig:simple_regret}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width = 16.5cm, height = 13cm]{matlab_figures/sensitivity_fric.eps}
\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Random, UCB, Thompson, Gittins). Graph is averaged over 100 shapes from the Brown Sillohoute Dataset \cite{brown} with a set $|G|=1000$ for each shape. As you can see the Thompson and Gittins method converge almost a magnitude faster than random allocation. UCB does poorly on simple regret which is expected \cite{best_arm}}
\vspace*{-10pt}
\label{fig:simple_regret}
\end{figure*}
